---
title: "Multiple Linear Regression"
output: html_document
---

```{r, setup, message=FALSE, include = FALSE}

#Load packages
fht::lib_fht()

#Read in data
data<- readr::read_rds("clean_data.rds")

```


```{r, include = FALSE}

efficacy_tbl<- data %>% dplyr::select(end_pseq_total, ref_pcs_total, ref_pseq_total, ref_bpi_pain_severity, ref_bpi_sleep,  ref_bpi_walking, ref_dass_depression, ref_dass_anxiety, ref_dass_stress, ref_daily_morphine, wait_time, age, pain_source, service_frequency_pain, compensation_case) %>% dplyr::mutate_if(is.character, as.factor)

```

# Initial Data Split

```{r}
efficacy_split<- rsample::initial_split(efficacy_tbl, prop = 3/4)

efficacy_split

```
# Allocate Training & Testing Data
```{r}

efficacy_train_tbl<- efficacy_split %>% rsample::training()

efficacy_test_tbl<- efficacy_split %>% rsample::testing()

```

# Define Recipe

```{r}
efficacy_recipe<- recipes::recipe(end_pseq_total ~ ., data = efficacy_tbl) %>% 
  recipes::step_dummy(recipes::all_nominal()) %>% 
  recipes::step_knnimpute(recipes::all_predictors())

#View recipe
summary(efficacy_recipe)

```


# View Pre-Processed Data

```{r, warning = FALSE}

efficacy_preprocessed<- efficacy_recipe %>% 
  recipes::prep(efficacy_train_tbl) %>% 
  recipes::juice()

#Look
efficacy_preprocessed %>% dplyr::glimpse()

```

# Remove All Pain Source Variables Except One

```{r}

efficacy_recipe<- efficacy_recipe %>% 
  recipes::step_rm(tidyselect::contains("pain_source"), -contains("work.school"))
  
```

# Prepare the Recipe (Estimate Means)

```{r}
efficacy_prepped<- efficacy_recipe %>% recipes::prep(data = efficacy_train_tbl)
```


# Apply the Preproessing Steps to the Model


```{r}

train_baked<- recipes::bake(efficacy_prepped, new_data = efficacy_train_tbl)
test_baked<- recipes::bake(efficacy_prepped, new_data = efficacy_test_tbl)

```

# Fit the Model to **Training** Data

```{r}

lr_model<- parsnip::linear_reg(mode = "regression") %>% 
  parsnip::set_engine("lm") %>% 
  parsnip::fit(end_pseq_total ~ ., data = train_baked)
  
  
```


#  Calculate Predictions Using **Test** Data

```{r}
 pred<- lr_model %>% 
  stats::predict(new_data = test_baked) 
  
```


# Calculate CIs Around Predictions Using New Data

```{r}
 conf_int_pred<- lr_model %>% 
  stats::predict(new_data = test_baked, type = "conf_int") 

```


# Combine Test Data Set with Model Predictions & CIs

```{r}
lm_predictions<- test_baked %>% 
  dplyr::bind_cols(pred) %>% 
  dplyr::bind_cols(conf_int_pred)

#View Actual, Predicted & CIs

lm_predictions %>% dplyr::select(end_pseq_total, .pred, .pred_lower, .pred_upper)

```

# Plot Actual Vs. Predicted Values

```{r}
ggplot(lm_predictions, aes(x = .pred, y = end_pseq_total)) + 
  geom_point(color = tidyquant::palette_light()[[1]]) + geom_smooth(color = tidyquant::palette_light()[[3]], se = FALSE) +
  geom_errorbar(aes(ymin = .pred_lower, 
                    ymax = .pred_upper),width = .2, color = tidyquant::palette_light()[[2]]) + tidyquant::theme_tq() + ylab("Pain Self-Efficacy - Actual") + xlab("Pain Self-Efficacy Predicted")
```


# Assess Model Performance

```{r}
yardstick::metrics(lm_predictions, truth = end_pseq_total, estimate = .pred)

```

# Addendum: Linear Regression For Inference

## Generate Data 

```{r}
inf_tbl<- data %>% dplyr::select(end_pseq_total, ref_pcs_total, ref_bpi_pain_severity, ref_daily_morphine, age, compensation_case) 

```

## Apply Transformations to Data As Needed

```{r}
inf_recipe<- recipes::recipe(end_pseq_total ~ ., data = inf_tbl) %>% 
  recipes::step_meanimpute(recipes::all_predictors())
```

## Retrieve the Processed Data

```{r}
inf_processed_tbl<- inf_recipe %>% 
  recipes::prep(inf_tbl) %>% 
  recipes::juice()
  
```

## Fit the Model to Data

```{r}

inf_model<- parsnip::linear_reg(mode = "regression") %>% 
  parsnip::set_engine("lm") %>% 
  parsnip::fit(end_pseq_total ~ ., data = inf_processed_tbl)
  
  
```


# Detour: Accessing Regression Results for Inferential Analysis

#### View Model Parameter Estimates

```{r}

inf_model$fit %>% broomExtra::tidy_parameters() %>% fht::dt_tab()

```

## Plot Coefficients

```{r}

ggstatsplot::ggcoefstats(inf_model$fit)

```

#### View Performance Indices

```{r}

inf_model$fit %>% broomExtra::glance_performance() %>% fht::dt_tab()

```

#### Generate Key Statistics To Assess Model Assumptions Later

```{r}
inf_model$fit %>% broomExtra::augment() %>% fht::dt_tab()

```



```{r, child="_session_info.Rmd"}
```